Chlorophylla

### 2019-08-06 Chlorophyll.Rmd
Chlorophyll

# Loading the data
load("Data/MODIS_Chloro.RData") # Extracted chlorophyll data
load("Data/site_list_sub.RData") # Site list of all the sites along the west coast

@@

# chloro_match %>%
#   filter(date == max(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = chloro))
# 
# chloro_sites <- chloro_match %>%
#   left_join(pixel_match, by = c("combi", "lon", "lat")) %>% 
#   dplyr::mutate(date = as.Date(date))
# # save(chloro_sites, file = "Data_P1/chloro_sites.RData")
# 
# # Visualisation
# load("Data_P1/chloro_sites.RData")
# Chloro_plot_complete <- ggplot(chloro_sites, aes(x = date, y = chloro)) +
#   geom_line() +
#   facet_wrap(~site, ncol = 1)
# Chloro_plot_complete
# 
# # Study period from 2010 - 2014
# chloro_data <- chloro_sites %>% 
#   filter(year(date) %in% seq(2010, 2014))
# # save(chloro_data, file = "Data_P1/chloro_data.RData")
# 
# # Plotting only years 2014-2015
# load("Data_P1/chloro_data.RData")
# Chloro_plot_filtered <- ggplot(chloro_data, aes(x = date, y = chloro)) +
#   geom_line() +
#   facet_wrap(~site, ncol = 1)
# Chloro_plot_filtered

# Creating daily temperatures
load("Data_P1/chloro_data.RData") # Loading in the chlorophyll-a data

daily_chloro <- chloro_data %>%
  # dplyr::mutate(date = as.Date(date)) %>% 
  dplyr::group_by(combi, lon, lat, date) %>%
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>%
  dplyr::group_by(combi, lon, lat) %>% 
  drop_na() %>% 
  tidyr::nest() %>%
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                     climatologyPeriod = c("2010-02-11", "2014-12-20"),
                     maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
  dplyr::select(-data) %>%
  tidyr::unnest() %>%
  select(-doy, -seas, -thresh)

>>>>

# Loading the data
load("Data/MODIS_Chloro.RData") # Extracted chlorophyll data
load("~/Documents/Masters_2019/Upwelling_MCS/Data/site_list_sub.Rdata") # Site list of all the sites along the west coast

@@

# chloro_match %>%
#   filter(date == max(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = chloro))
# 
chloro_sites <- chloro_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat")) %>%
  dplyr::mutate(date = as.Date(date))
save(chloro_sites, file = "Data/chloro_sites.RData")

# # Visualisation
load("Data/chloro_sites.RData")
# Chloro_plot_complete <- ggplot(chloro_sites, aes(x = date, y = chloro)) +
#   geom_line() +
#   facet_wrap(~site, ncol = 1)
# Chloro_plot_complete

# Creating daily temperatures
daily_chloro <- chloro_sites %>%
  # dplyr::mutate(date = as.Date(date)) %>% 
  dplyr::group_by(combi, lon, lat, date) %>%
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>%
  dplyr::group_by(combi, lon, lat) %>% 
  drop_na() %>% 
  tidyr::nest() %>%
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                     climatologyPeriod = c("2010-02-11", "2014-12-20"),
                     maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
  dplyr::select(-data) %>%
  tidyr::unnest() %>%
  select(-doy, -seas, -thresh)
